MLCommons Earthquake Science Benchmark

### 2022-02-19 paper-capstone-earthquake.tex
update hw table for desktop

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:my_label}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|ll|r|l|l|l|l|l|}
        \hline
        Section & Organization   & Machine                         & & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL    & Aurora & \cite{www-aurora}         &              &                  & & & &    ??? 2022   \\ \hline
         \ref{id:ornl}  & ORNL   & Summit &\cite{www-summit}         &        27000 & \nvidia{volta}     & & & &               \\ \hline
         \ref{id:nersc} & NERSC  & Perlmutter & \cite{www-perlmutter} &         6000 & \nvidia{A100}      & & & & Jan 2022      \\ \hline
         \ref{id:sdsc}  & SDSC   & Expanse & \cite{www-expanse}       &          200 & \nvidia{V100}
         SMX2 & & & &               \\ \hline
         \ref{id:uva}   & UVA    & Rivanna &\cite{www-rivanna}       &            8 & \nvidia{A100}      & 80GB & ? & &  Feb 2022      \\
            &    &  &       &            8 & \nvidia{A100}      & 40GB & 8 & &       \\
            &    &  &       &            ? & \nvidia{RTX3090}   & 24GB & ? & ? & 2021          \\
            &    &  &       &            ? & \nvidia{K80}       & 11GB & 8 & 9 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 16GB & 4 & 1 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 32GB & 4 & 12 & 2021          \\
            &    &  &       &            ? & \nvidia{P100}      & 12GB & 4 & 3 & 2021          \\
            &    &  &       &            ? & \nvidia{RTX2080TI} & 11GB & 10 & 2 & 2021          \\
         \hline
         \ref{id:ral}   & RAL    & Pearl &\cite{www-pearl-1}         &           16 & \nvidia{V100}      & & & &  \\ \hline
         \ref{id:dgx}   & Fox    & DGX Station A100 &\cite{www-dgx-station-a100} & 4 & \nvidia{A100}      & 80GB & 4 & 1 & May 2021      \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:my_label}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|r|l|l|l|l|l|}
        \hline
        Section & Organization   & Machine                         & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:gcomputer}   & 
         Gregor    & 
         5950X   &  
         1 &   
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         1 & 
         1 & 
         Sep 2021   \\
            & 
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         1 & 
         1 & 
         Feb 2022   \\
         \hline
         \ref{id:tcomputer}   & Thomas.A  & i7-8750H &  1 &   NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{id:t2computer}   & Thomas.B  & i7-7700HQ &  1 &   NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

>>>>

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:hwoverview}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|ll|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL    & Aurora & \cite{www-aurora}         &              &                  & & & &    ??? 2022   \\ \hline
         \ref{id:ornl}  & ORNL   & Summit &\cite{www-summit}         &        27000 & \nvidia{volta}     & & & &               \\ \hline
         \ref{id:nersc} & NERSC  & Perlmutter & \cite{www-perlmutter} &         6000 & \nvidia{A100}      & & & & Jan 2022      \\ \hline
         \ref{id:sdsc}  & SDSC   & Expanse & \cite{www-expanse}       &          200 & \nvidia{V100}
         SMX2 & & & &               \\ \hline
         \ref{id:uva}   & UVA    & Rivanna &\cite{www-rivanna}       &            8 & \nvidia{A100}      & 80GB & ? & &  Feb 2022      \\
            &    &  &       &            8 & \nvidia{A100}      & 40GB & 8 & &       \\
            &    &  &       &            ? & \nvidia{RTX3090}   & 24GB & ? & ? & 2021          \\
            &    &  &       &            ? & \nvidia{K80}       & 11GB & 8 & 9 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 16GB & 4 & 1 & 2021          \\
            &    &  &       &            ? & \nvidia{V100}      & 32GB & 4 & 12 & 2021          \\
            &    &  &       &            ? & \nvidia{P100}      & 12GB & 4 & 3 & 2021          \\
            &    &  &       &            ? & \nvidia{RTX2080TI} & 11GB & 10 & 2 & 2021          \\
         \hline
         \ref{id:ral}   & RAL    & Pearl &\cite{www-pearl-1}         &           16 & \nvidia{V100}      & & & &  \\ \hline
         \ref{id:dgx}   & Fox    & DGX Station A100 &\cite{www-dgx-station-a100} & 4 & \nvidia{A100}      & 80GB & 4 & 1 & May 2021      \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\TODO{Add your personal computers to this table \url{https://github.com/Data-ScienceHub/mlcommons-science/issues/37}}
\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:desktops}
    \centering
%\begin{adjustbox}{angle=90}
\begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{|r|l|l|r|l|l|l|l|l|}
        \hline
        See also & Organization   & Machine                         & Processors    & GPUs             & \makecell{Memory\\/Device} &  \makecell{GPU\\/Device} & \makecell{No. of\\ nodes} & Commissioned \\ 
        \hline
        \hline
         Table \ref{tab:gcompute}   & 
         Gregor    & 
         5950X   &  
         1 &   
         \href{https://www.gigabyte.com/Graphics-Card/GV-N307TGAMING-OC-8GD#kf}{GIGABYTE Gaming RTX 3070TI}  & 
         8GB & 
         1 & 
         1 & 
         Sep 2021   \\
            & 
            & 
            &  
            &   
         \href{https://rog.asus.com/us/graphics-cards/graphics-cards/rog-strix/rog-strix-rtx3090-o24g-gaming-model/}{ASUS ROG Strix RTX 3090} & 
         24GB & 
         1 & 
         1 & 
         Feb 2022   \\
         \hline
         \ref{sec:tcomputer}   & Thomas.A  & i7-8750H &  1 &   NVIDIA GeForce RTX 2070 with Max-Q Design  & 16GB & 1 & 1 & 2019   \\
         \hline
         \ref{sec:t2computer}   & Thomas.B  & i7-7700HQ &  1 &   NVIDIA GeForce GTX 1060  & 16GB & 1 & 1 & 2017   \\
         \hline
    \end{tabular}
    \end{adjustbox}
\end{table*}

@@

\input{machines}
